Generating Hubbard Model Solutions from Anderson Impurity Model Solutions

### 2021-08-23 notes.tex
added some figures

This Hamiltonian is, however, explicitly asymmetric between the sites 0 and 1 (the effective bath couples only to 1). To rectify that, we will symmetrize the coupling between the effective bath and the sites 0 and 1, by exchanging the sites 0 and 1. The resultant Hamiltonian is

@@

\(H^D(0,1)\) is the Hubbard dimer Hamiltonian:

@@

This Hubbard dimer is shown in fig.~\ref{hubb-dim}.
	\caption{Correlated asymmetric Anderson molecule schematic version. It consists of two sites, impurity(blue) and zero mode(green). The impurity site has onsite repulsion, and their is inter-site hopping.}

@@

	\includegraphics[width=0.6\textwidth]{hubb_dim.png}

@@

>>>>

	\caption{Correlated asymmetric Anderson molecule schematic version. It consists of an impurity site (blue) hybridising with a bath (ring) by hopping into and out of the zeroth site (pink). The other sites (green) form the rest of the bath. Just the impurity site and the zeroth site have onsite repulsion.}
This Hamiltonian is depicted in fig.~\ref{and_mol}. Such a Hamiltonian is, however, explicitly asymmetric between the sites 0 and 1 (the effective bath couples only to 1). To rectify that, we will symmetrize the coupling between the effective bath and the sites 0 and 1, by exchanging the sites 0 and 1. The resultant Hamiltonian is

@@

\(H^D(0,1)\) is the Hubbard dimer Hamiltonian (shown in fig.~\ref{hubb-dim}):

@@

@@

	\includegraphics[width=0.4\textwidth]{hubb_dim.png}

@@

This entire procedure is depicted in fig.~\ref{dimer-bath}.
	\includegraphics[width=0.8\textwidth]{dimer_bath.png}
	\caption{The process of symmetrizing the Rg fixed point Hamiltonian and then creating a dimer+bath Hamiltonian.}
	\label{dimer-bath}
